The SMT Competition 2015--2018

### 2018-10-08 2018/report/SMT-COMP.tex
FLoC Olympic Games (work in progress)

In 2014, the SMT Competition was part of the FLoC Olympic Games, which
sponsored three Kurt G\"odel medals.  After substantial internal
debate, the competition organizers decided to award these to the
winner of the QF\_BV logic (which has historically been the logic with
the largest number of solver submissions), as well as to the two best
main-track solvers according to a competition-wide ranking that had
been instituted especially for this
purpose~\cite{DBLP:journals/jsat/CokDW14}.

The 2018 edition of the competition was again part of the FLoC Olympic
Games.  After last-minute negotiations with the Olympic Games
organizers, it was decided that the SMT Competition would award seven
Kurt G\"odel medals.  The competition organizers gave these to the
following solvers:
\begin{itemize}
\item The best three main-track solvers according to the
  competition-wide scoring (first place: CVC4, second place:
  Yices-2.6.0, third place: SMTInterpol);
\item the solver that won the most competitive divisions in the
  application track (Yices-2.6.0);
\item the solver that won the most competitive divisions in the
  unsat-core track (Yices-2.6.0);
\item the solver(s) that won the QF\_BV division in the main track
  (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT)
\end{itemize}

The competition-wide ranking that was used in~2018 was a refinement of
the ranking scheme introduced in~2014.  A contentious issue has been
the treatment of incorrect solver results in this ranking.  While
incorrect answers cause a solver to be ranked behind all correct
solvers in the per-division ranking (see \TODO )

\section{Post-Competition Activity}
\label{sec:post}

>>>>

In 2014, the SMT Competition was part of the FLoC Olympic Games.
These gave the competition increased visibility and sponsored three
Kurt G\"odel medals.  After substantial internal debate, the 2014
competition organizers decided to award these to the winner of the
main track's QF\_BV division (which has historically been the logic
with the largest number of solver submissions), as well as to the two
best main-track solvers according to a competition-wide ranking that
had been instituted especially for this
purpose~\cite{DBLP:journals/jsat/CokDW14}.  This ranking emphasizes
breadth of solver participation---a solver participating in many
logics need not be the best in any one of them to rank highly.

The competition-wide ranking for the main track was retained and
refined after~2014.  A contentious issue in this ranking has been the
scoring of incorrect solver responses.  In the per-division rankings,
an incorrect response causes a solver to be ranked behind all correct
solvers~\cite{rules18}.  But the competition's main track consists of
many independent divisions.  To balance the strong interest in correct
solvers against the risk of stifling innovation, the competition-wide
ranking was revised in~2017 to use a fixed numeric penalty for each
division with incorrect responses.  The value of this penalty is
chosen so that entering a (possibly buggy) solver that can solve all
benchmarks into a division has a positive expected score if the
probability of a soundness bug in the solver is below~$20\,\%$.

The 2018 edition of the competition was again part of the FLoC Olympic
Games.  After last-minute negotiations with the Olympic Games
organizers, it was decided that the SMT Competition would award seven
Kurt G\"odel medals.  The 2018 competition organizers conferred these
to the following solvers:
\begin{itemize}
\item The best three main-track solvers according to the
  competition-wide scoring (first place: CVC4, second place:
  Yices-2.6.0, third place: SMTInterpol);
\item the solver(s) that won the QF\_BV division in the main track
  (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT);
\item the solver that won the most competitive divisions in the
  application track (Yices-2.6.0);
\item the solver that won the most competitive divisions in the
  unsat-core track (Yices-2.6.0).
\end{itemize}

\begin{tjark}
  Discuss competition-wide rankings for application and unsat-core
  tracks.
\end{tjark}
